%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  %---------------------------------------------------------
  \cventry
  {Senior Software Engineer} % Job title
  {Fountain} % Organization
  {San Francisco, CA, USA} % Location
  {Sept. 2021 - Jan. 2023} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Improved CI/CD times by 66\% and 50\% for the two most frequently changed and tested repositories.}
      \item {Replicated previous cloud infrastructure in Azure to ensure a resilient and fault tolerant multi-cloud application.}
      \item {Implemented a centralized and secured environment variable management service for all deployed services/applications.}
      \item {Implemented a runtime analysis tool for unused code that led to the removal of close to 100,000 LOC from our primary application repository.}
    \end{cvitems}
  }

  %---------------------------------------------------------

  \cventry
  {Associate Senior Software Engineer} % Job title
  {Cerner} % Organization
  {Kansas City, MO, USA} % Location
  {Feb. 2021 - Sept. 2021} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Develop and maintain an organization-wide Ruby on Rails API platform that handles ~365 million requests per week for hospitals and clinics worldwide, aggregated across multiple geographical and logical zones.}
      \item {Designed and developed a Ruby on Rails rate limiting service to protect the platform and the services behind it due to a high volume of requests, increasing overall availability across the platform.}
      \item {Improved monitoring and observability to our web platform by creating a Lua library to communicate telemetry data from the platform to New Relic for analysis and alerts on platform health.}
      \item {Answer questions and drive discussion regarding adherence to platform standards like the OpenAPI Specification, Ruby on Rails best practices, and applicable RFCs.}
      \item {Mentor new engineers and evaluate whether they are prepared for their permanent team assignment.}
      \item {Created an frontend UI in React.js for internal consumers to easily manage how they rate limit their individual APIs.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Software Engineer} % Job title
  {Cerner} % Organization
  {Kansas City, MO, USA} % Location
  {Aug. 2018 - Feb. 2021} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Led initiative to decouple the weekly platform deployment testing from the functional validation, integration testing, and prototyping of our contributors' APIs via a Jenkins job and loadbalancer configuration, saving thousands of engineering hours to date.}
      \item {Implemented a distroless Docker image that eliminated hundreds of CVEs from unused system packages provided by default in the OS image.}
      \item {Transitioned from a WEBrick server to the Openresty web platform with an NGINX web server in order to remove a bottleneck for high volume POST endpoints and streaming resources (upload and download).}
      \item {Identified and managed Service Level Objectives (SLOs) and Service Level Indicators (SLIs) to set a baseline expectation for all APIs incorporated into our platform.}
      \item {Monitor, support, and resolve metrics alerts from various telemetry sources, scheduled tenant migrations, and incidents related to the platform.}
      \item {Maintain and curate platform and services' documentation for external consumers.}
      \item {Simplified and centralized our API Developer Guide and platform contribution process to eliminate unnecessary paperwork.}
      \item {Developed New Relic dashboard and alert templates using Terraform modules to improve monitoring scalability when deploying to new cloud region zones.}
      \item {Responsible for platform health, support, and incident response while on-call and as escalation manager.}
    \end{cvitems}
  }

  %---------------------------------------------------------
\end{cventries}

% critical/core platform
% mentoring/intern, improve culture, URI standards
% organizing engineers for gov post deployment testing
