%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Associate Senior Software Engineer} % Job title
    {Cerner} % Organization
    {Kansas City, MO, USA} % Location
    {Feb. 2021 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Develop and maintain an organization-wide Ruby on Rails API platform that handles ~365 million requests per week for hospitals and clinics worldwide aggregated across multiple geographical and logical zones.}
        \item {Designed and developed a Ruby on Rails rate limiting service to protect the platform and the services behind it from a high volume of requests, increasing overall availability across the platform.}
        \item {Created an npm package in React.js that was integrated into an internal application for engineering teams to quickly and easily manage how they set rate limits to protect their services.}
        \item {Improved monitoring and observability to our web platform by creating a Lua library to communicate telemetry data from the API platform to New Relic for analysis and alerts on platform health.}
        \item {Mentor new engineers and formally evaluate whether they are prepared for their permanent team assignment.}
        \item {Answer questions and drive discussion in a public forum regarding adherence to standards like the OpenAPI Specification, Ruby on Rails best practices, and applicable RFCs.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Cerner} % Organization
    {Kansas City, MO, USA} % Location
    {Aug. 2018 - Feb. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led initiative to decouple the weekly platform deployment testing from the functional validation, integration testing, and prototyping of our contributors' APIs via a Jenkins job and loadbalancer configuration, saving thousands of engineering hours to date.}
        \item {Implemented a distroless Docker image that eliminated hundreds of CVEs from unused system packages provided by default in the OS image.}
        \item {Transitioned from a WEBrick server to the Openresty web platform with an NGINX web server in order to remove a bottleneck for high volume POST endpoints and streaming resources (upload and download).}
        \item {Identified and managed Service Level Objectives (SLOs) and Service Level Indicators (SLIs) to set a baseline expectation for all APIs incorporated into our platform.}
        \item {Monitor, support, and resolve metrics alerts from various telemetry sources, scheduled tenant migrations, and incidents related to the platform.}
        \item {Maintain and curate platform and services' documentation for external consumers.}
        \item {Simplified and centralized our API Developer Guide and platform contribution process to eliminate unnecessary paperwork.}
        \item {Developed New Relic dashboard and alert templates using Terraform modules to improve the continuous delivery process when deploying to new cloud region zones.}
        \item {Responsible for platform health, support, weekly deployments, and incident response while on-call and as escalation manager.}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}

% organizing engineers for gov post deployment testing
